---
title: "clear white space"
author: "Kamarul Imran Musa"
date: "11/4/2018"
output:
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

\newpage


```{r, echo=FALSE, message=FALSE}
library(png)
library(grid)
library(magick)
```

# Fig 1

ssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssvvvvssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssvvssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssv

```{r, echo=FALSE, fig.height = 6, fig.width = 6, fig.cap = "plot without setting the right raster output size"}
mycat <- readPNG('cat.png')
grid.raster(mycat)
```

ssssssssssssssssssssssssssssssssssssssssssvvvvssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssss

\newpage

```{r, echo=FALSE}
# imagecat <- image_read(mycat)
# print(imagecat)
# 235/400
# height/width = 0.59
```

\newpage

# Fig 2

ssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssvvvvssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssvvssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssv

```{r , echo= FALSE, fig.cap = "plot with correct margin, square size", fig.asp=0.59}
library(png)
library(grid)
mycat <- readPNG('cat.png')
grid.raster(mycat)
```

ssssssssssssssssssssssssssssssssssssssssssvvvvssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssss

Ref : <https://stackoverflow.com/questions/32748235/how-to-remove-white-space-above-and-below-image-in-r-markdown?answertab=votes#tab-top>